Cities as they could be: Artificial Life and Urban Systems

### 2022-08-30 Docs/Papers/ALifeCities/arxiv/v1/paper.tex
reviews_alife2020_alifecities

% ALife approaches to urban systems
% Bibliometrics
% Urban complexity

@@

%\cite{doi:10.1098/rstb.2019.0329}

@@

%%%%%%%%%%
\begin{figure*}
\begin{center}
\begin{mdframed}
\includegraphics[width=\linewidth]{figures/core.png}
\end{mdframed}
\begin{mdframed}
\includegraphics[width=\linewidth]{figures/corealife_zoom.png}
\end{mdframed}
\caption{Citation networks for Artificial Life and Artificial Intelligence applications to urban systems. Full core citation network (top panel) and ALife subnetwork (bottom panel). Network visualization is done with the Gephi software, spatialization with a Force Atlas 2 algorithm, node label size corresponds to node degree. Colors correspond to communities obtained with the Louvain algorithm.\label{fig:citnw}}
\end{center}
\end{figure*}
%%%%%%%%%%

@@

%%%%%%%%%%
\begin{figure*}
\vspace{-1cm}
\begin{center}
\includegraphics[width=0.49\linewidth]{figures/citation_all.png}
\includegraphics[width=0.49\linewidth]{figures/citation_alife.png}
\caption{Citation flows between largest communities, for the full network (Left) and the ALife subnetwork (Right). Scale color is given by a renormalized logarithmic scale (the major share of citations being internal to communities), the maximal flow being 0.95 (resp. 0.98) for the full network (resp. the ALife subnetwork) and the minimal flow $4.8\cdot 10^{-5}$ (resp. $1.9 \cdot 10^{-4}$). Dendograms show a hierarchical clustering following the proximity matrix.\label{fig:flows}}
\end{center}
\end{figure*}
%%%%%%%%%%

@@

\footnotesize
\bibliographystyle{apalike}
\bibliography{biblio} % replace by the name of your .bib file

>>>>

@@

@@

%%%%%%%%%%
\begin{figure*}
\begin{center}
\begin{mdframed}
\includegraphics[width=\linewidth]{core.png}
\end{mdframed}
\begin{mdframed}
\includegraphics[width=\linewidth]{corealife_zoom.png}
\end{mdframed}
\caption{Citation networks for Artificial Life and Artificial Intelligence applications to urban systems. Full core citation network (top panel) and ALife subnetwork (bottom panel). Network visualization is done with the Gephi software, spatialization with a Force Atlas 2 algorithm, node label size corresponds to node degree. Colors correspond to communities obtained with the Louvain algorithm.\label{fig:citnw}}
\end{center}
\end{figure*}
%%%%%%%%%%

@@

%%%%%%%%%%
\begin{figure*}
\vspace{-1cm}
\begin{center}
\includegraphics[width=0.49\linewidth]{citation_all.png}
\includegraphics[width=0.49\linewidth]{citation_alife.png}
\caption{Citation flows between largest communities, for the full network (Left) and the ALife subnetwork (Right). Scale color is given by a renormalized logarithmic scale (the major share of citations being internal to communities), the maximal flow being 0.95 (resp. 0.98) for the full network (resp. the ALife subnetwork) and the minimal flow $4.8\cdot 10^{-5}$ (resp. $1.9 \cdot 10^{-4}$). Dendograms show a hierarchical clustering following the proximity matrix.\label{fig:flows}}
\end{center}
\end{figure*}
%%%%%%%%%%

@@

\footnotesize
%\bibliographystyle{apalike}
%\bibliography{biblio} % replace by the name of your .bib file

\begin{thebibliography}{}

\bibitem[Adamowski and Karapataki, 2010]{adamowski2010comparison}
Adamowski, J. and Karapataki, C. (2010).
\newblock Comparison of multivariate regression and artificial neural networks
  for peak urban water-demand forecasting: evaluation of different ann learning
  algorithms.
\newblock {\em Journal of Hydrologic Engineering}, 15(10):729--743.

\bibitem[Aguilar et~al., 2014]{aguilar2014past}
Aguilar, W., Santamar{\'\i}a-Bonfil, G., Froese, T., and Gershenson, C. (2014).
\newblock The past, present, and future of artificial life.
\newblock {\em Frontiers in Robotics and AI}, 1:8.

\bibitem[Akbarzadeh et~al., 2006]{akbarzadeh2006towards}
Akbarzadeh, A., Frahm, J.-M., Mordohai, P., Clipp, B., Engels, C., Gallup, D.,
  Merrell, P., Phelps, M., Sinha, S., Talton, B., et~al. (2006).
\newblock Towards urban 3d reconstruction from video.
\newblock In {\em Third International Symposium on 3D Data Processing,
  Visualization, and Transmission (3DPVT'06)}, pages 1--8. IEEE.

\bibitem[Banzhaf et~al., 2016]{banzhaf2016defining}
Banzhaf, W., Baumgaertner, B., Beslon, G., Doursat, R., Foster, J.~A.,
  McMullin, B., De~Melo, V.~V., Miconi, T., Spector, L., Stepney, S., et~al.
  (2016).
\newblock Defining and simulating open-ended novelty: requirements, guidelines,
  and challenges.
\newblock {\em Theory in Biosciences}, 135(3):131--161.

\bibitem[Batty, 2018]{batty2018inventing}
Batty, M. (2018).
\newblock {\em Inventing future cities}.
\newblock Mit Press.

\bibitem[Batty and Marshall, 2009]{batty2009centenary}
Batty, M. and Marshall, S. (2009).
\newblock Centenary paper: The evolution of cities: Geddes, abercrombie and the
  new physicalism.
\newblock {\em Town Planning Review}, 80(6):551--574.

\bibitem[Batty and Xie, 1994]{batty1994cells}
Batty, M. and Xie, Y. (1994).
\newblock From cells to cities.
\newblock {\em Environment and planning B: Planning and design},
  21(7):S31--S48.

\bibitem[Blondel et~al., 2008]{blondel2008fast}
Blondel, V.~D., Guillaume, J.-L., Lambiotte, R., and Lefebvre, E. (2008).
\newblock Fast unfolding of communities in large networks.
\newblock {\em Journal of statistical mechanics: theory and experiment},
  2008(10):P10008.

\bibitem[Bourgine and Stewart, 2004]{bourgine2004autopoiesis}
Bourgine, P. and Stewart, J. (2004).
\newblock Autopoiesis and cognition.
\newblock {\em Artificial life}, 10(3):327--345.

\bibitem[Bull et~al., 2000]{bull2000meme}
Bull, L., Holland, O., and Blackmore, S. (2000).
\newblock On meme--gene coevolution.
\newblock {\em Artificial life}, 6(3):227--235.

\bibitem[Casti, 1997]{casti1997would}
Casti, J.~L. (1997).
\newblock Would-be worlds: toward a theory of complex systems.
\newblock {\em Artificial Life and Robotics}, 1(1):11--13.

\bibitem[Chen and Cheng, 2010]{chen2010review}
Chen, B. and Cheng, H.~H. (2010).
\newblock A review of the applications of agent technology in traffic and
  transportation systems.
\newblock {\em IEEE Transactions on intelligent transportation systems},
  11(2):485--497.

\bibitem[Cottineau et~al., 2017]{cottineau2017diverse}
Cottineau, C., Hatna, E., Arcaute, E., and Batty, M. (2017).
\newblock Diverse cities or the systematic paradox of urban scaling laws.
\newblock {\em Computers, environment and urban systems}, 63:80--94.

\bibitem[Davids, 2002]{davids2002urban}
Davids, A. (2002).
\newblock Urban search and rescue robots: from tragedy to technology.
\newblock {\em IEEE Intelligent systems}, 17(2):81--83.

\bibitem[Doursat et~al., 2012]{doursat2012morphogenetic}
Doursat, R., Sayama, H., and Michel, O. (2012).
\newblock {\em Morphogenetic engineering: toward programmable complex systems}.
\newblock Springer.

\bibitem[D’Acci, 2013]{d2013simulating}
D’Acci, L. (2013).
\newblock Simulating future societies in isobenefit cities: Social isobenefit
  scenarios.
\newblock {\em Futures}, 54:3--18.

\bibitem[Flack and Krakauer, 2011]{flack2011challenges}
Flack, J.~C. and Krakauer, D.~C. (2011).
\newblock Challenges for complexity measures: A perspective from social
  dynamics and collective social computation.
\newblock {\em Chaos: An Interdisciplinary Journal of Nonlinear Science},
  21(3):037108.

\bibitem[Franklin, 2002]{franklin2002embodied}
Franklin, S. (2002).
\newblock {\em Embodied progress: A cultural account of assisted conception}.
\newblock Routledge.

\bibitem[Gonz{\'a}lez et~al., 2015]{gonzalez2015review}
Gonz{\'a}lez, D., P{\'e}rez, J., Milan{\'e}s, V., and Nashashibi, F. (2015).
\newblock A review of motion planning techniques for automated vehicles.
\newblock {\em IEEE Transactions on Intelligent Transportation Systems},
  17(4):1135--1145.

\bibitem[Ib{\'a}{\~n}ez et~al., 2011]{ibanez2011using}
Ib{\'a}{\~n}ez, A., Larra{\~n}aga, P., and Bielza, C. (2011).
\newblock Using bayesian networks to discover relationships between
  bibliometric indices. a case study of computer science and artificial
  intelligence journals.
\newblock {\em Scientometrics}, 89(2):523--551.

\bibitem[IEPSFC, 2018]{iepsfc2018science}
IEPSFC (2018).
\newblock Science and the future of cities, report of the international expert
  panel on science and the future of cities.
\newblock Technical report.

\bibitem[Kato et~al., 1998]{kato1998alife}
Kato, N., Okuno, T., Okano, A., Kanoh, H., and Nishihara, S. (1998).
\newblock An alife approach to modeling virtual cities.
\newblock In {\em SMC'98 Conference Proceedings. 1998 IEEE International
  Conference on Systems, Man, and Cybernetics (Cat. No. 98CH36218)}, volume~2,
  pages 1168--1173. IEEE.

\bibitem[Kato et~al., 2000]{kato2000modeling}
Kato, N., Okuno, T., Suzuki, R., and Kanoh, H. (2000).
\newblock Modeling virtual cities based on interaction between cells.
\newblock In {\em Smc 2000 conference proceedings. 2000 ieee international
  conference on systems, man and cybernetics.'cybernetics evolving to systems,
  humans, organizations, and their complex interactions'(cat. no. 0}, volume~1,
  pages 143--148. IEEE.

\bibitem[Kendoul, 2012]{kendoul2012survey}
Kendoul, F. (2012).
\newblock Survey of advances in guidance, navigation, and control of unmanned
  rotorcraft systems.
\newblock {\em Journal of Field Robotics}, 29(2):315--378.

\bibitem[Kim and Cho, 2006]{kim2006comprehensive}
Kim, K.-J. and Cho, S.-B. (2006).
\newblock A comprehensive overview of the applications of artificial life.
\newblock {\em Artificial Life}, 12(1):153--182.

\bibitem[Langton, 1986]{langton1986studying}
Langton, C.~G. (1986).
\newblock Studying artificial life with cellular automata.

\bibitem[Levinson et~al., 2011]{levinson2011towards}
Levinson, J., Askeland, J., Becker, J., Dolson, J., Held, D., Kammel, S.,
  Kolter, J.~Z., Langer, D., Pink, O., Pratt, V., et~al. (2011).
\newblock Towards fully autonomous driving: Systems and algorithms.
\newblock In {\em 2011 IEEE Intelligent Vehicles Symposium (IV)}, pages
  163--168. IEEE.

\bibitem[Leydesdorff, 2001]{leydesdorff2001challenge}
Leydesdorff, L. (2001).
\newblock {\em The challenge of scientometrics: The development, measurement,
  and self-organization of scientific communications}.
\newblock Universal-Publishers.

\bibitem[Lobo et~al., 2020]{lobo2020urban}
Lobo, J., Alberti, M., Allen-Dumas, M., Arcaute, E., Barthelemy, M.,
  Bojorquez~Tapia, L.~A., Brail, S., Bettencourt, L., Beukes, A., Chen, W.-Q.,
  et~al. (2020).
\newblock Urban science: Integrated theory from the first cities to sustainable
  metropolises.

\bibitem[Lucic and Teodorovic, 2002]{lucic2002transportation}
Lucic, P. and Teodorovic, D. (2002).
\newblock Transportation modeling: an artificial life approach.
\newblock In {\em 14th IEEE International Conference on Tools with Artificial
  Intelligence, 2002.(ICTAI 2002). Proceedings.}, pages 216--223. IEEE.

\bibitem[Lv et~al., 2014]{lv2014traffic}
Lv, Y., Duan, Y., Kang, W., Li, Z., and Wang, F.-Y. (2014).
\newblock Traffic flow prediction with big data: a deep learning approach.
\newblock {\em IEEE Transactions on Intelligent Transportation Systems},
  16(2):865--873.

\bibitem[Ma et~al., 2009]{ma2009real}
Ma, Y., Chowdhury, M., Sadek, A., and Jeihani, M. (2009).
\newblock Real-time highway traffic condition assessment framework using
  vehicle--infrastructure integration (vii) with artificial intelligence (ai).
\newblock {\em IEEE Transactions on Intelligent Transportation Systems},
  10(4):615--627.

\bibitem[Medda et~al., 2009]{medda2009morphogenetic}
Medda, F., Nijkamp, P., and Rietveld, P. (2009).
\newblock A morphogenetic perspective on spatial complexity.
\newblock In {\em Complexity and spatial networks}, pages 51--60. Springer.

\bibitem[Nicosia et~al., 2009]{nicosia2009extending}
Nicosia, V., Mangioni, G., Carchiolo, V., and Malgeri, M. (2009).
\newblock Extending the definition of modularity to directed graphs with
  overlapping communities.
\newblock {\em Journal of Statistical Mechanics: Theory and Experiment},
  2009(03):P03024.

\bibitem[Niu et~al., 2016]{niu2016global}
Niu, J., Tang, W., Xu, F., Zhou, X., and Song, Y. (2016).
\newblock Global research on artificial intelligence from 1990--2014:
  Spatially-explicit bibliometric analysis.
\newblock {\em ISPRS International Journal of Geo-Information}, 5(5):66.

\bibitem[Olsen, 1982]{olsen1982urban}
Olsen, S. (1982).
\newblock Urban metabolism and morphogenesis.
\newblock {\em Urban Geography}, 3(2):87--109.

\bibitem[Openshaw, 1995]{openshaw1995developing}
Openshaw, S. (1995).
\newblock Developing automated and smart spatial pattern exploration tools for
  geographical information systems applications.
\newblock {\em Journal of the Royal Statistical Society: Series D (The
  Statistician)}, 44(1):3--16.

\bibitem[Pelechano et~al., 2007]{pelechano2007controlling}
Pelechano, N., Allbeck, J.~M., and Badler, N.~I. (2007).
\newblock Controlling individual agents in high-density crowd simulation.

\bibitem[Pumain, 2018]{pumain2018evolutionary}
Pumain, D. (2018).
\newblock An evolutionary theory of urban systems.
\newblock In {\em International and transnational perspectives on urban
  systems}, pages 3--18. Springer.

\bibitem[Raimbault, 2018]{raimbault2018calibration}
Raimbault, J. (2018).
\newblock Calibration of a density-based model of urban morphogenesis.
\newblock {\em PloS one}, 13(9).

\bibitem[Raimbault, 2019a]{raimbault2019exploration}
Raimbault, J. (2019a).
\newblock Exploration of an interdisciplinary scientific landscape.
\newblock {\em Scientometrics}, 119(2):617--641.

\bibitem[Raimbault, 2019b]{raimbault2019modeling}
Raimbault, J. (2019b).
\newblock Modeling interactions between transportation networks and
  territories: a co-evolution approach.
\newblock {\em arXiv preprint arXiv:1902.04802}.

\bibitem[Raimbault et~al., 2020]{raimbault2020spatial}
Raimbault, J., Broere, J., Somveille, M., Serna, J.~M., Strombom, E., Moore,
  C., Zhu, B., and Sugar, L. (2020).
\newblock A spatial agent based model for simulating and optimizing networked
  eco-industrial systems.
\newblock {\em Resources, Conservation and Recycling}, 155:104538.

\bibitem[Raimbault et~al., 2019]{raimbault2019empowering}
Raimbault, J., Chasset, P.-O., Cottineau, C., Commenges, H., Pumain, D.,
  Kosmopoulos, C., and Banos, A. (2019).
\newblock Empowering open science with reflexive and spatialised indicators.
\newblock {\em Environment and Planning B: Urban Analytics and City Science},
  page 2399808319870816.

\bibitem[Raimbault and Perret, 2019]{raimbault2019generating}
Raimbault, J. and Perret, J. (2019).
\newblock Generating urban morphologies at large scales.
\newblock In {\em The 2019 Conference on Artificial Life}, pages 179--186. MIT
  Press.

\bibitem[Rigas et~al., 2014]{rigas2014managing}
Rigas, E.~S., Ramchurn, S.~D., and Bassiliades, N. (2014).
\newblock Managing electric vehicles in the smart grid using artificial
  intelligence: A survey.
\newblock {\em IEEE Transactions on Intelligent Transportation Systems},
  16(4):1619--1635.

\bibitem[Sayama, 2019]{doi:10.1162/isala00134}
Sayama, H. (2019).
\newblock Suppleness and open-endedness for social sustainability.
\newblock {\em Artificial Life Conference Proceedings}, (31):28--29.

\bibitem[Schipperijn et~al., 2010]{schipperijn2010factors}
Schipperijn, J., Ekholm, O., Stigsdotter, U.~K., Toftager, M., Bentsen, P.,
  Kamper-J{\o}rgensen, F., and Randrup, T.~B. (2010).
\newblock Factors influencing the use of green space: Results from a danish
  national representative survey.
\newblock {\em Landscape and urban planning}, 95(3):130--137.

\bibitem[Sen-Ching and Kamath, 2004]{sen2004robust}
Sen-Ching, S.~C. and Kamath, C. (2004).
\newblock Robust techniques for background subtraction in urban traffic video.
\newblock In {\em Visual Communications and Image Processing 2004}, volume
  5308, pages 881--892. International Society for Optics and Photonics.

\bibitem[Siqueiros-García, 2019]{doi:10.1162/isala00135}
Siqueiros-García, J.~M. (2019).
\newblock Cities, a conceptual framing for a synthetic perspective.
\newblock {\em Artificial Life Conference Proceedings}, (31):30--31.

\bibitem[Squazzoni and Casnici, 2013]{squazzoni2013social}
Squazzoni, F. and Casnici, N. (2013).
\newblock Is social simulation a social science outstation? a bibliometric
  analysis of the impact of jasss.
\newblock {\em Journal of Artificial Societies and Social Simulation},
  16(1):10.

\bibitem[Takizawa et~al., 2000]{takizawa2000simulation}
Takizawa, A., Kawamura, H., and Tani, A. (2000).
\newblock Simulation of urban system``as it could be''by multiagent model.
\newblock In {\em Computing in Civil and Building Engineering (2000)}, pages
  1566--1573.

\bibitem[Taylor~Buck, 2017]{taylor2017art}
Taylor~Buck, N. (2017).
\newblock The art of imitating life: The potential contribution of biomimicry
  in shaping the future of our cities.
\newblock {\em Environment and Planning B: Urban Analytics and City Science},
  44(1):120--140.

\bibitem[Thrun and Montemerlo, 2006]{thrun2006graph}
Thrun, S. and Montemerlo, M. (2006).
\newblock The graph slam algorithm with applications to large-scale mapping of
  urban structures.
\newblock {\em The International Journal of Robotics Research},
  25(5-6):403--429.

\bibitem[Torrens, 2003]{torrens2003automata}
Torrens, P.~M. (2003).
\newblock Automata-based models of urban systems.
\newblock {\em Advanced spatial analysis}, pages 61--79.

\bibitem[Van~Raan and Tijssen, 1993]{van1993neural}
Van~Raan, A. and Tijssen, R. (1993).
\newblock The neural net of neural network research: An exercise in
  bibliometric mapping.
\newblock {\em Scientometrics}, 26(1):169--192.

\bibitem[Vlahogianni et~al., 2005]{vlahogianni2005optimized}
Vlahogianni, E.~I., Karlaftis, M.~G., and Golias, J.~C. (2005).
\newblock Optimized and meta-optimized neural networks for short-term traffic
  flow prediction: A genetic approach.
\newblock {\em Transportation Research Part C: Emerging Technologies},
  13(3):211--234.

\bibitem[Votsis and Haavisto, 2019]{votsis2019urban}
Votsis, A. and Haavisto, R. (2019).
\newblock Urban dna and sustainable cities: A multi-city comparison.
\newblock {\em Frontiers in Environmental Science}, 7:4.

\bibitem[Wang, 2007]{wang2007toward}
Wang, F.-Y. (2007).
\newblock Toward a paradigm shift in social computing: The acp approach.
\newblock {\em IEEE Intelligent Systems}, 22(5):65--67.

\bibitem[White and Engelen, 1993]{white1993cellular}
White, R. and Engelen, G. (1993).
\newblock Cellular automata and fractal urban form: a cellular modelling
  approach to the evolution of urban land-use patterns.
\newblock {\em Environment and planning A}, 25(8):1175--1199.

\bibitem[White, 1989]{white1989artificial}
White, R.~W. (1989).
\newblock The artificial intelligence of urban dynamics: Neural network
  modeling of urban structure.
\newblock In {\em Papers of the Regional Science Association}, volume~67, pages
  43--53. Springer.

\bibitem[Whitelaw, 2004]{whitelaw2004metacreation}
Whitelaw, M. (2004).
\newblock {\em Metacreation: art and artificial life}.
\newblock Mit Press.

\bibitem[Wu and Silva, 2010]{wu2010artificial}
Wu, N. and Silva, E.~A. (2010).
\newblock Artificial intelligence solutions for urban land dynamics: a review.
\newblock {\em Journal of Planning Literature}, 24(3):246--265.

\bibitem[Zheng et~al., 2014]{zheng2014urban}
Zheng, Y., Capra, L., Wolfson, O., and Yang, H. (2014).
\newblock Urban computing: concepts, methodologies, and applications.
\newblock {\em ACM Transactions on Intelligent Systems and Technology (TIST)},
  5(3):1--55.

\end{thebibliography}

### 2022-08-30 Docs/Papers/ALifeCities/paper/paper.tex
papers
reviews_alife2020_alifecities

\documentclass[letterpaper]{article}

\usepackage{natbib,alifeconf}  %% The order is important

% *****************
%  Requirements:
% *****************
%
% - All pages sized consistently at 8.5 x 11 inches (US letter size).
% - PDF length <= 8 pages for full papers, <=2 pages for extended
%    abstracts (not including citations).
% - Abstract length <= 250 words.
% - No visible crop marks.
% - Images at no greater than 300 dpi, scaled at 100%.
% - Embedded open type fonts only.
% - All layers flattened.
% - No attachments.
% - All desired links active in the files.

% Note that the PDF file must not exceed 5 MB if it is to be indexed
% by Google Scholar. Additional information about Google Scholar
% can be found here:
% http://www.google.com/intl/en/scholar/inclusion.html.

% If your system does not generate letter format documents by default,
% you can use the following workflow:
% latex example
% bibtex example
% latex example ; latex example
% dvips -o example.ps -t letterSize example.dvi
% ps2pdf example.ps example.pdf

% For pdflatex users:
% The alifeconf style file loads the "graphicx" package, and
% this may lead some users of pdflatex to experience problems.
% These can be fixed by editing the alifeconf.sty file to specify:
% \usepackage[pdftex]{graphicx}
%   instead of
% \usepackage{graphicx}.
% The PDF output generated by pdflatex should match the required
% specifications and obviously the dvips and ps2pdf steps become
% unnecessary.

% Note:  Some laser printers have a serious problem printing TeX
% output. The use of ps type I fonts should avoid this problem.

@@

\title{\vspace{-2cm}Cities as they could be: Artificial Life and Urban Systems}
\author{Juste Raimbault$^{1,2,3}$\\
\mbox{}\\
$^1$Center for Advanced Spatial Analysis, University College London\\
$^2$UPS CNRS 3611 ISC-PIF\\
$^3$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\\
juste.raimbault@polytechnique.edu} % email of corresponding author

% For several authors from the same institution use the same number to
% refer to one address.
%
% If the names do not fit well on one line use
%         Author 1, Author 2 ... \\ {\Large\bf Author n} ...\\ ...
%
% If the title and author information do not fit in the area
% allocated, place \setlength\titlebox{<new height>} after the
% \documentclass line where <new height> is 2.25in

\begin{document}
\maketitle

\begin{abstract}
% Abstract length should not exceed 250 words
The metaphor of cities as organisms has a long history in urban planning, and a few urban modeling approaches have explicitly been linked to Artificial Life. We propose in that paper to explore the extent of Artificial Life and Artificial Intelligence application to urban issues, by constructing and exploring a citation network of around 225,000 papers. It shows that most of the literature is indeed application of methodologies and a rather strong modularity of approaches. We finally develop ALife concepts which have a strong potential for the development of new urban theories.
\end{abstract}

@@

\cite{doi:10.1098/rstb.2019.0329}

>>>>

\documentclass[10pt]{article}

\usepackage{natbib}
\usepackage[margin=2cm]{geometry}

@@

\title{Cities as they could be: Artificial Life and Urban Systems}
\author{Juste Raimbault$^{1,2,3}$\\
\mbox{}\\
$^1$Center for Advanced Spatial Analysis, University College London\\
$^2$UPS CNRS 3611 ISC-PIF\\
$^3$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\\
juste.raimbault@polytechnique.edu}

% reviews [01/06/2020]
% Dear Submitters and Authors,

%Thank you for your submission to ALife 2020. Please see below for reviews on your submissions.

%SUBMISSION: 76
%TITLE: Cities as they could be: Artificial Life and Urban Systems

%----------------------- REVIEW 1 ---------------------
%SUBMISSION: 76
%TITLE: Cities as they could be: Artificial Life and Urban Systems
%AUTHORS: Juste Raimbault

%----------- Overall evaluation -----------
%SCORE: 1 (weak accept)
%----- TEXT:
%This is a useful synthesis of the existing literature on the crossover between alife and urbanism. As populations increasingly move to cities, coming up with new and creative ways of handling this transition will become a more pressing problem, so this analysis is timely.

%The list of possible areas for development is well-motivated and useful.

%With regards to the keywords chosen for the bibliometric analysis - how specific are these? I experimented by typing "artificial life urban" into Google Scholar (the engine used here), and got a reasonable number of hits on papers that I would not necessarily expect to consider to be in scope... (e.g., "The urban matrix and artificial light restricts the nightly ranging behaviour of Gould's long‐eared bat (Nyctophilus gouldi)") Why not "artificial life" as a phrase, rather than as individual terms?.... So, my confidence in the analysis is very slightly undermined... The author does state that they manually removed some "obviously" irrelevant papers, but this clearly introduces a degree of subjectivity... However, the overall results would appear to be reasonably robust...

%I would like the diagrams to be slightly more readable (specifically, Fig 1), although I appreciate the constraints on presentation.

%----------------------- REVIEW 2 ---------------------
%SUBMISSION: 76
%TITLE: Cities as they could be: Artificial Life and Urban Systems
%AUTHORS: Juste Raimbault

%----------- Overall evaluation -----------
%SCORE: -2 (reject)
%----- TEXT:
%This paper presents a bibliometric analysis of literature at the intersection of artificial intelligence, artificial life, and urban systems. 225,000 papers are identified, and their citation networks are presented. Then, some analysis describes communities within these research areas, and identifies 'flows' of citations (i.e. implying transference of ideas) between them.

%The paper describes its methodology well, and the analysis provides some interesting things of note. However, the scope of the search is quite vague and arbitrary ('urban' and 'artificial intelligence' are included, but not 'city' or 'machine learning', for example) and any actionable insights for ALife researchers are not sufficiently present for me to judge that the paper yet has publishable value for the community.

%Additionally, the paper unfortunately has quite a few language errors that make it difficult to understand in places. I would recommend obtaining feedback from a copy editor.

%----------------------- REVIEW 3 ---------------------
%SUBMISSION: 76
%TITLE: Cities as they could be: Artificial Life and Urban Systems
%AUTHORS: Juste Raimbault
%
%----------- Overall evaluation -----------
%SCORE: 1 (weak accept)
%----- TEXT:
%Summary:
%In this paper, the authors explore the Artificial Life and Intelligence methodologies, tools, concepts, and application domains to enhance the understanding and management of cities.
%Their exploration method consists of literature mapping of nearly 225,000 papers in different research areas related to ALife or/and AI. 
%The result is a list of distinct communities and domains related to ALife and AI concepts, the relation between them and how each community uses ALife and AI applications and concepts in general and particularly in urban systems. After the bibliometric analysis, they also develop several concepts which are considered to be under-explored in the literature.

%Contribution to science:
%The main contribution of this paper is the Network Graph linking all the communities using ALife and AI concepts and more importantly the sub Network that emphasizes the use of ALife in urban systems. 
%This contribution is interesting because it can be considered as a taxonomy in the field of ALife in Urban Systems.

%The shortcomings in this paper are stated as follows:
%- Errors in typography, in the abstract line 03 : "We propose in this paper", not "in that paper".
%- Errors in typography, in the introduction line 19 : "It is", not "is is"
%- The first figure representing the Network Graph of the citation network for ALife and AI applications to urban systems is not readable, it contains too much text.

%The biggest faults are stated as follows:
%- Artificial Intelligence concepts are presented briefly without any further detail (e.g, Neural Networks)
%- The use cases of AI mentioned in the paper are shallow and not clear (e.g, AI can be applied to manage highway traffic)
%- The use of vague expressions when stating AI which keeps the subject broad and unreachable (e.g, We saw tools and methods, in particular Artificial Intelligence methods, are already widely applied)

%Verdict:
%It is an interesting work because it provides a good bibliometric analysis and makes clear the existing correlation between communities related to urban systems and using ALife concepts. This paper may be considered as a starting point for further exploration and concept development but the scientific contribution is weak.

\begin{document}

\maketitle

\begin{abstract}
The metaphor of cities as organisms has a long history in urban planning, and a few urban modeling approaches have explicitly been linked to Artificial Life. We propose in that paper to explore the extent of Artificial Life and Artificial Intelligence application to urban issues, by constructing and exploring a citation network of around 225,000 papers. It shows that most of the literature is indeed application of methodologies and a rather strong modularity of approaches. We finally develop ALife concepts which have a strong potential for the development of new urban theories.
\end{abstract}

% ALife approaches to urban systems
% Bibliometrics
% Urban complexity

@@

%\cite{doi:10.1098/rstb.2019.0329}
